### 2016-03-31 Chapters/paper1.tex
Added intro chapter (commented PDF images)

Consider the 1$D$ transport equation 
\begin{equation}
\label{eq-eqtr}
u_t-u_x=0,
\end{equation}
in the interval $[0,1]$ with periodic boundary conditions and the following pulse as initial condition:
\begin{equation}\label{eq-trinc}
u_0(x) = \left\{
\begin{array}{ll}
1 & \textrm{if } x\in[0.25,0.75],\\
0 & \textrm{otherwise}.
\end{array}\right.
\end{equation}
% SB note: Check this figure: 1) No stab is not a good label... one would think no stab but you have put nonlinear GJV stab... Next, SZ and SZ3 are not appropriate labels. We should use NPS (nodal proj stab) and NPS+GJV (w/ shock capturing)... and explain every method in the text... We have called the NPS stab and now we call SZ stab... non consistent
% Labels should be clearly stated in the caption of the figure.
This test is being used to show the positive effect of the combined use of linear stabilization with a shock-capturing technique. At this point, the definition of the shock-capturing technique, namely nGJV or bGJV in Algorithm \ref{alg-wNPS-GJV}, is not important since both definitions reduce to the one in \cite{burman_nonlinear_2007} for the 1$D$ case. In Fig. \Fig{pulse1} we show the results obtained when solving this problem with $200$ FEs and using the Crank-Nicolson time integration  with CFL $0.5$, a semi-implicit treatment of the nonlinearity and no mass lumping. Let us recall that the monotonic methods preserve the DMP when no mass lumping is performed. The parameters used in the GJV stabilization are $c_{\rm gjv} = \tilde c_{\rm gjv} =0.5$ (which is the minimum value for which the strong DMP property holds) and $q=10$. It is clear that the combination of the artificial diffusion and the weighted NPS stabilization with GJV shock-capturing outperforms each of them separately. One can observe in the right part of Fig. \Fig{pulse1} the terracing effect on the solution obtained when no linear stabilization is used.
\begin{figure}
\centering
\subfigure[Results for GJV shock-capturing, NPS stabilization and both combined with weighting (wNPS-GJV). ]{\includegraphics[width=9.65cm]{Figures/paper1/test20_p1_200.pdf}} %
\subfigure[Terracing effect.]{\includegraphics[clip=true, trim=3.8cm 0cm 3.1cm 0cm,width=4.35cm]{Figures/paper1/test20_p1_200_d2.pdf}} %
\caption{Test 1. GJV with $c_{\rm gjv}=0.5$, $q=10$, $p=1$ and $N=200$, Crank-Nicolson, CFL=0.5 and no mass lumping.}\label{fig-pulse1}
\end{figure}

The same test can be used to check the dependence of the DMP property on the variable $c_{\rm gjv}$ in the transport problem.  For this test, we have used the explicit forward Euler method for the integration in time with mass lumping and a CFL of $0.01$ in such a way that the error of the integration in time can be neglected. Fig. \Fig{SZ_AD_2} shows the results obtained when solving problem \Eq{eqtr}-\Eq{trinc} with  wNPS-GJV in Algorithm \ref{alg-wNPS-GJV}. We notice that the larger the value of $q$ the sharper are the oscillations that appear for $c_{\rm gjv} < 0.5$, so we have used $q=100$ to show the results. It is clear that the threshold $c_{\rm gjv} = 0.5$ is sharp; overshoots and undershoots appear in the solution when $c_{\rm gjv}$ is slightly smaller than $0.5$, violating the TVD property.
  %The results obtained using the SC without any linear stabilization are displayed in Fig. \ref{tttPure_AD}. As we expected $\nu = 0.5$ is a threshold for the DMP property. Moreover, in order to avoid the error of the integration in time we have used CFL$=0.01$.
\begin{figure}%
\centering
\subfigure[$c_{\rm gjv}  = 0.49,0.5,0.51$]{\includegraphics[width=7cm]{Figures/paper1/BurmanSZ.pdf} %
\label{fig-SZ_AD_2_s1} }%
\subfigure[Detail of \subref{fig-SZ_AD_2_s1}]{\includegraphics[width=7cm]{Figures/paper1/BurmanSZ1d.pdf}  }%
\caption{Test 1. GJV with $c_{\rm gjv}=0.5$, $q=100$, $p=1$ and $N=100$. Forward Euler with CFL$=0.01$ and mass lumping.}\label{fig-SZ_AD_2}%
\end{figure}

@@

\begin{figure}
\includegraphics[clip=true, trim=0cm 9cm 0cm 9cm,width=14cm]{Figures/paper1/smooth_conv_test_2D.pdf}%
 \caption{Test 2. $L^2(\Omega)$ error vs size of the mesh. Crank-Nicolson, $t=1$, $\Delta t = 10^{-3}$. No Mass lumping.}\label{fig-smooth_sol}
 \end{figure}

@@

\begin{figure}%
\centering
\subfigure[${\rm osc(t)}$ in time]{\includegraphics[clip=true,  trim=3cm 9cm 4cm 9cm,width=7.9cm]{Figures/paper1/osc_time_tr.pdf}\label{fig-osc}}%
%\subfigure[${\rm osc(t)}$ in time]{\includegraphics[clip=true,  trim=3cm 9cm 4cm 9cm,width=7.9cm]{Figures/paper1/osc_time_tr_new.pdf}}%
\subfigure[{SUPG-RV, $t = 0.01 $}]{\includegraphics[clip=true, trim=1.6cm 11cm 1.6cm 3cm,width=7.9cm]{Figures/paper1/15_SUPG_RV_T_001.png}\label{fig-osrv}}\\%
\caption{Test 3. Evolution of the parameter ${\rm osc}$. Detail of the solution for the SUPG-RV at $t=0.01$. Space discretization with $p=1$ and $250\times 250 \times 2$ triangular mesh. Crank-Nicolson, $\Delta t = 2 \cdot 10^{-4}$ and no mass lumping.}\label{fig-osctime}
\end{figure}

>>>>

Consider the 1$D$ transport equation 
\begin{equation}
\label{eq-eqtr}
u_t-u_x=0,
\end{equation}
in the interval $[0,1]$ with periodic boundary conditions and the following pulse as initial condition:
\begin{equation}\label{eq-trinc}
u_0(x) = \left\{
\begin{array}{ll}
1 & \textrm{if } x\in[0.25,0.75],\\
0 & \textrm{otherwise}.
\end{array}\right.
\end{equation}
% SB note: Check this figure: 1) No stab is not a good label... one would think no stab but you have put nonlinear GJV stab... Next, SZ and SZ3 are not appropriate labels. We should use NPS (nodal proj stab) and NPS+GJV (w/ shock capturing)... and explain every method in the text... We have called the NPS stab and now we call SZ stab... non consistent
% Labels should be clearly stated in the caption of the figure.
This test is being used to show the positive effect of the combined use of linear stabilization with a shock-capturing technique. At this point, the definition of the shock-capturing technique, namely nGJV or bGJV in Algorithm \ref{alg-wNPS-GJV}, is not important since both definitions reduce to the one in \cite{burman_nonlinear_2007} for the 1$D$ case. In Fig. \Fig{pulse1} we show the results obtained when solving this problem with $200$ FEs and using the Crank-Nicolson time integration  with CFL $0.5$, a semi-implicit treatment of the nonlinearity and no mass lumping. Let us recall that the monotonic methods preserve the DMP when no mass lumping is performed. The parameters used in the GJV stabilization are $c_{\rm gjv} = \tilde c_{\rm gjv} =0.5$ (which is the minimum value for which the strong DMP property holds) and $q=10$. It is clear that the combination of the artificial diffusion and the weighted NPS stabilization with GJV shock-capturing outperforms each of them separately. One can observe in the right part of Fig. \Fig{pulse1} the terracing effect on the solution obtained when no linear stabilization is used.
%\begin{figure}
%\centering
%\subfigure[Results for GJV shock-capturing, NPS stabilization and both combined with weighting (wNPS-GJV). ]{\includegraphics[width=9.65cm]{Figures/paper1/test20_p1_200.pdf}} %
%\subfigure[Terracing effect.]{\includegraphics[clip=true, trim=3.8cm 0cm 3.1cm 0cm,width=4.35cm]{Figures/paper1/test20_p1_200_d2.pdf}} %
%\caption{Test 1. GJV with $c_{\rm gjv}=0.5$, $q=10$, $p=1$ and $N=200$, Crank-Nicolson, CFL=0.5 and no mass lumping.}\label{fig-pulse1}
%\end{figure}

The same test can be used to check the dependence of the DMP property on the variable $c_{\rm gjv}$ in the transport problem.  For this test, we have used the explicit forward Euler method for the integration in time with mass lumping and a CFL of $0.01$ in such a way that the error of the integration in time can be neglected. Fig. \Fig{SZ_AD_2} shows the results obtained when solving problem \Eq{eqtr}-\Eq{trinc} with  wNPS-GJV in Algorithm \ref{alg-wNPS-GJV}. We notice that the larger the value of $q$ the sharper are the oscillations that appear for $c_{\rm gjv} < 0.5$, so we have used $q=100$ to show the results. It is clear that the threshold $c_{\rm gjv} = 0.5$ is sharp; overshoots and undershoots appear in the solution when $c_{\rm gjv}$ is slightly smaller than $0.5$, violating the TVD property.
  %The results obtained using the SC without any linear stabilization are displayed in Fig. \ref{tttPure_AD}. As we expected $\nu = 0.5$ is a threshold for the DMP property. Moreover, in order to avoid the error of the integration in time we have used CFL$=0.01$.
%\begin{figure}%
%\centering
%\subfigure[$c_{\rm gjv}  = 0.49,0.5,0.51$]{\includegraphics[width=7cm]{Figures/paper1/BurmanSZ.pdf} %
%\label{fig-SZ_AD_2_s1} }%
%\subfigure[Detail of \subref{fig-SZ_AD_2_s1}]{\includegraphics[width=7cm]{Figures/paper1/BurmanSZ1d.pdf}  }%
%\caption{Test 1. GJV with $c_{\rm gjv}=0.5$, $q=100$, $p=1$ and $N=100$. Forward Euler with CFL$=0.01$ and mass lumping.}\label{fig-SZ_AD_2}%
%\end{figure}

@@

%\begin{figure}
%\includegraphics[clip=true, trim=0cm 9cm 0cm 9cm,width=14cm]{Figures/paper1/smooth_conv_test_2D.pdf}%
 %\caption{Test 2. $L^2(\Omega)$ error vs size of the mesh. Crank-Nicolson, $t=1$, $\Delta t = 10^{-3}$. No Mass lumping.}\label{fig-smooth_sol}
 %\end{figure}

@@

%\begin{figure}%
%\centering
%\subfigure[${\rm osc(t)}$ in time]{\includegraphics[clip=true,  trim=3cm 9cm 4cm 9cm,width=7.9cm]{Figures/paper1/osc_time_tr.pdf}\label{fig-osc}}%
%\subfigure[{SUPG-RV, $t = 0.01 $}]{\includegraphics[clip=true, trim=1.6cm 11cm 1.6cm 3cm,width=7.9cm]{Figures/paper1/15_SUPG_RV_T_001.png}\label{fig-osrv}}\\%
%\caption{Test 3. Evolution of the parameter ${\rm osc}$. Detail of the solution for the SUPG-RV at $t=0.01$. Space discretization with $p=1$ and $250\times 250 \times 2$ triangular mesh. Crank-Nicolson, $\Delta t = 2 \cdot 10^{-4}$ and no mass lumping.}\label{fig-osctime}
%\end{figure}
